\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Abstract

	\begin{abstract}
\spacingset{1.45}
        A geometric interpretation is developed for so-called {\em reconciliation} methodologies used to forecast time series that adhere to known linear constraints.  In particular, a general framework is established nesting many existing popular reconciliation methods within the class of {\em projections}.  This interpretation facilitates the derivation of novel results that explain why and how reconciliation via projection is guaranteed to improve forecast accuracy with respect to a specific class of loss functions.  The result is also demonstrated empirically.  The geometric interpretation is further used to provide a new proof that forecast reconciliation results in unbiased forecasts as long as the initial so-called {\em base} forecasts are also unbiased.  Approaches for dealing with biased base forecasts are proposed and explored in an extensive empirical study on Australian tourism flows.  Overall, the method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.

>>>>

\begin{abstract}
\spacingset{1.45}
  A geometric interpretation is developed for so-called \emph{reconciliation} methodologies used to forecast time series that adhere to known linear constraints. In particular, a general framework is established nesting many existing popular reconciliation methods within the class of \emph{projections}. This interpretation facilitates the derivation of novel results that explain why and how reconciliation via projection is guaranteed to improve forecast accuracy with respect to a specific class of loss functions. The result is also demonstrated empirically. The geometric interpretation is further used to provide a new proof that forecast reconciliation results in unbiased forecasts provided the initial \emph{base} forecasts are also unbiased. Approaches for dealing with biased base forecasts are proposed and explored in an extensive empirical study on Australian tourism flows. Overall, the method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.
